---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LGPclassifiers

<!-- badges: start -->
<!-- badges: end -->

This package contains all the in-house implemented classifiers for the LGP project.
For the moment it includes Reddy Cell Origin classifier
(both the original implementation published [here](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5659841/) and a single-sample implemented version).

## Installation

You can install the latest released version of LGPclassifiers like so:

```{r, eval=FALSE}
my_repos <- c(
  "CRAN" = "https://cran.rstudio.com/",
  "BMS RSPM" = "https://pm.rdcloud.bms.com/bms-cg-biogit-bran/latest"
)
options(repos = my_repos)
install.packages("LGPclassifiers")
```

You can install the dev version:

```{r, eval = FALSE}
remotes::install_git(
  "git@github.com:bms-ips/KSR-LGPclassifiers.git",
  ref = "dev",
  git = "external"
)
```

## Example

Run Reddy COO classifier or the internal single-sample version using a reference dataset (ssREFERENCE) as follows:

```{r example, eval=FALSE}
library(LGPclassifiers)

# Read query TPM matrix (colSums ~ 10^6)
# All three input formats ENSGs, ENSTs & Hugo names are acceptable
query.tpm <- readRDS("ensembl91-genes.salmon-tpm file from NGS360")

# Run original implementation of Reddy COO classifier
reddy <- computeCOO(query = query.tpm, useReference = F)

# Run internal Reddy COO classifier on reference-normalized samples
ssREFERENCE <- computeCOO(query = query.tpm, useReference = T)

```
